Invariant Generation using ACDL

### 2016-08-07 invariant.tex
highlights of ACDCL

\subsection{Highlights of ACDCL-P}
\begin{enumerate}
\item decision heuristics on cond variables enable us to prove many 
programs without actually deciding on the actual program variables. This 
leads to significantly less number of decisions and less number of conflicts 
compared to the SAT solver. Further, decisions on conditional program 
variables can be seen as simulating path-based symbolic execution. But when 
a decision on conditional varaible leads to BOTTOM, ACDCL-P tried to learn 
the reason for failure, and hence can also be seen similar to IMPACT like
algorithm. 
\item Last UIP allows us to learn clauses that has more information in it. 
\item Compared to pure AI based tools, ACDCL-P performs program and property 
driven partitioning with simpler domains to prove programs with relational 
properties (branch7). AI based tool would require richer domains like 
relational (equality) domain to prove such programs. 
\item Compared to cdfpl, our tool proves more programs correctly and works on 
non-numeric programs as well.
\item Chaotic propagations help ACDCL-P to generate stronger deductions and reach 
fixpoint early in propagation stage.
\item Compared to cdfpl, acdl solver is agnostic to abstract domain. cdfpl
stores the value of variables (from interval domain) in every decision 
and deduction stage in a container "value". So, cdfpl keeps track of literals 
and their intervals at every stage which makes it difficult to extend it to other 
richer domains. However, ACDCL-P treat literals as meet irreducibles. Hence, 
ACDCL-P can be easily extended to other richer domains.    
\item ACDCL-P handles loops by automatic invariant generation.
\end{enumerate}

@@

\item Whereas, ACDCL-P stores the deduction information from the AI phase into the 
trail. In such case, the entries in the trail does not have a corresponding
reason clause. Thus, it is not possible to perform resolution proof to find the 
UIP since the propagation trail does not store such information.   
\end{enumerate}

@@

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{sat}{sat}
\SetKwData{unsat}{unsat}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Formula $\mathcal{F}$}
\Output{The status (\sat or \unsat or \unknown)}
%\tcc{The initial state}
%$ACDL \leftarrow \tuple{\neg(assert(c)),loopselect=nondet}$ \nllabel{algline:initPS}\;
result=\deduce(F)\;
\uIf{$result == \perp$} {
  \return \unsat \;
}
\uElse
{
  $t$ = get\_counterexample\_trace\_from\_P \;
  \uIf{spurious\_check(t)}
  {
    \return \sat \;
  }
}
\While{$true$} 
{
  meet\_irreducible = decision\_heuristics($F$)\;
  decision\_container = decision\_container $\cup$ meet\_irreducible\; 
  \uIf{meet\_irreducible == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    \assign result=\deduce(F)\;
    \uIf{result == UNKNOWN}
    {
      $t$ = get\_counterexample\_trace\_from\_P \;
      \uIf{spurious\_check(t)}
      {
        \return \sat \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{result == PASS} {
        \uIf{$\neg$ conflict\_analysis()} {
          return \unsat \;  
        }
        \assign result=\deduce(F)\;
      }
    }
  }
}
\end{small}
\caption{ACDCL Solver \label{Alg:acdl}}
\end{algorithm2e}

>>>>

\subsection{Highlights of ACDCL-P}
\begin{enumerate}
\item decision heuristics on cond variables enable us to prove many 
programs without actually deciding on the actual program variables. This 
leads to significantly less number of decisions and less number of conflicts 
compared to the SAT solver. Further, decisions on conditional program 
variables can be seen as simulating path-based symbolic execution. But when 
a decision on conditional varaible leads to BOTTOM, ACDCL-P tried to learn 
the reason for failure, and hence can also be seen similar to IMPACT like
algorithm. 
\item Last UIP allows us to learn clauses that has more information in it. 
\item Compared to pure AI based tools, ACDCL-P performs program and property 
driven partitioning with simpler domains to prove programs with relational 
properties (branch7). AI based tool would require richer domains like 
relational (equality) domain to prove such programs. 
\item Compared to cdfpl, our tool proves more programs correctly and works on 
non-numeric programs as well.
\item Chaotic propagations help ACDCL-P to generate stronger deductions and reach 
fixpoint early in propagation stage.
\item Compared to cdfpl, acdl solver is agnostic to abstract domain. cdfpl
stores the value of variables (from interval domain) in every decision 
and deduction stage in a container "value". So, cdfpl keeps track of literals 
and their intervals at every stage which makes it difficult to extend it to other 
richer domains. However, ACDCL-P treat literals as meet irreducibles. Hence, 
ACDCL-P can be easily extended to other richer domains.    
\item  ACDL computes learnt clause with UIP for octagon domains -- first time 
extension of learning in ACDL to richer relational domains.   
\item ACDCL-P handles loops by automatic invariant generation.
\end{enumerate}

@@

\item Whereas, ACDCL-P stores the deduction information from the AI phase into the 
trail. In such case, the entries in the trail does not have a corresponding
reason clause. Thus, it is not possible to perform resolution proof to find the 
UIP since the propagation trail does not store such information.

\item unitness is guaranteed in propagation in CDCL — that is all deduction are 
made through unit clause. Whereas, unitness is not guaranteed in propagation in 
ACDCL — that is deduction in AI phase are not made through unit clause, but deductions
made through conflict clause are only unit. Thus, resolution proof is not possible.

\end{enumerate}

@@

\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{decide}{Decide}
\SetKwFunction{deduce}{deduce}
\SetKwFunction{backtrack}{backtrack}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
\SetKwFunction{nondet}{nondet}
\SetKwFunction{run}{run}
\SetKwFunction{learn}{learn}
\SetKwFunction{continue}{continue}
\SetKwFunction{assign}{assign}
\SetKwRepeat{Do}{do}{while}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{safe}
\SetKwData{unsafe}{unsafe}
\SetKwData{sat}{sat}
\SetKwData{unsat}{unsat}
\SetKwData{unknown}{unknown}
\SetKwData{true}{true}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Formula $\mathcal{F}$}
\Output{The status (\sat or \unsat or \unknown)}
result=\deduce(F)\;
\uIf{$result == \perp$} {
  \return \unsat \;
}
\uElse
{
  $t$ = get\_satisfying\_assignment($F$) \;
  \uIf{spurious\_check(t)}
  {
    \return \sat \;
  }
}
\While{$true$} 
{
  meet\_irreducible = decision\_heuristics($F$)\;
  decision\_container = decision\_container $\cup$ meet\_irreducible\; 
  \uIf{meet\_irreducible == NULL}
  {
    return \unknown\; 
  }
  \uElse
  {
    \assign result=\deduce(F)\;
    \uIf{result == UNKNOWN}
    {
      $t$ = get\_satisfying\_assignment($F$) \;
      \uIf{spurious\_check(t)}
      {
        \return \sat \;
      }
      \uElse 
      {
        \continue\;
      }
    }
    \uElse
    {
      \Do{result == PASS} {
        \uIf{$\neg$ conflict\_analysis()} {
          return \unsat \;  
        }
        \assign result=\deduce(F)\;
      }
    }
  }
}
\end{small}
\caption{ACDCL Solver \label{Alg:acdl}}
\end{algorithm2e}
